\Large \bf Dynamic Program Dialysis with Lya

### 2020-01-11 paper/draft.tex
Update library

\heading{Library Interface Transformation}
Returning the library's value to its consumer comprises interpreting the library, linking it with the custom context, and applying a final transformation to its return value.
% TODO: (for intro!) ..to attenuate the privilege exercised by the library's consumer
The goal of the final transformation is to track activity at the boundary;
  for some analyses, \sys needs to also augment the values going through the library's interface---including continuation functions passed as arguments to the library's methods.

\subsection{Reassembly}
\label{three}

% \section{Applications of Analysis}
% \label{apps}

\section{Implementation: Lya}
\label{impl}

We implemented \sys for version 8.9.4 of the Node.js runtime.
Node.js is a runtime that bun

in about 1.5K lines of JavaScript.
We summarize where other implementations would diverge in table 1

Individual analysis are implemented using a set of templates that provide initial constructs (see below).
The difference between them, \ie the amount of code that is unique to each analysis, is about 20--30 lines.

>>>>

\heading{Library Interface Transformation}
Returning the library's value to its consumer comprises interpreting the library, linking it with the custom context, and applying a final transformation to its return value.
% TODO: (for intro!) ..to attenuate the privilege exercised by the library's consumer
The goal of the final transformation is to track activity at the boundary;
  for some analyses, \sys needs to additionally augment the values going through the library's interface---including continuation functions passed as arguments to the library's methods.

The final transformation is applied for every new consumer of the library.
This is because the system needs to distinguish between all different boundaries of the same library, explained in the next section~\sx{three}.

\subsection{Re-assembly}
\label{three}

To successfully reassemble the application, \sys needs to ensure that cross-references between libraries resolve correctly.
The central mechanism for resolution is the library cache.

To support multiple wrappers for a single cached library, the cache is extended by two levels reaching a total of three.
The reason for adding the two levels is that libraries are usually governed by a single context analysis but multiple interface analyses, one for each of their consumers.
A context transformation is applied at most a few times (usually only once), whereas a return-value transformation is applied on every \ttt{import}.
Thus, the first level is indexed by library identifiers (as before); the second by context analysis; and the third by analysis of the \ttt{export}ed interfaces.
% The first level is indexed by library identifiers as before, the second level is indexed by implicit segments, and the third level is indexed by explicit segments.
For each library, the second level contains a collection of entries corresponding to mostly-transformed libraries, and the third level contains fully transformed libraries.
Mostly-transformed libraries have gone through the entire transformation pipeline except for the last stage:
  they have been interpreted and have had their context transformed and linked, but their return value has not been processed to track analysis of its interface.

% A single augmented object (such as \ttt{Object}) may need to be shared among multiple files in a library, or even multiple libraries within a package directory.
A special entry is reserved the original library value~\sx{two}, so that subsequent transformations can skip loading the library from disk.
When a library is already loaded, \sys indexes by context analysis to retrieve the transformed library instance corresponding to this analysis.
It then applies a transformation to the library's return value.
New libraries are inserted into the second-level cache right after evaluation of the interpreted function.
